Who does big team science?

### 2023-08-29 manuscript_scopus.Rmd
typo

BTS appears to be expanding as a result of two sources: 1) increasing
globalization and technology that allows for real-time interdisciplinary
research, and 2) expanding interest in reproducibility, replication, and
generalizability [@maxwell2015; @nelson2018; @zwaan2018]. Technological
advances have provided easier ways to collaborate with people who are
from other universities and countries through document sharing platforms
(e.g., Google, GitHub, and the Open Science Framework), video chatting
platforms (e.g., Zoom, Microsoft Teams), and messaging and project
management platforms (e.g., Slack, Trello, when2meet, etc.). The
credibility movement seems to suggest that by having both collaborations
that span across the globe and subfields of research areas, age groups,
and education levels should help to drive science in the path of better
materials, reliability, generalizability and more robust sample sizes
(when necessary) in a study [@auspurg2021]; @nosek2014method;
@lebel2018].

>>>>

BTS appears to be expanding as a result of two sources: 1) increasing
globalization and technology that allows for real-time interdisciplinary
research, and 2) expanding interest in reproducibility, replication, and
generalizability [@maxwell2015; @nelson2018; @zwaan2018]. Technological
advances have provided easier ways to collaborate with people who are
from other universities and countries through document sharing platforms
(e.g., Google, GitHub, and the Open Science Framework), video chatting
platforms (e.g., Zoom, Microsoft Teams), and messaging and project
management platforms (e.g., Slack, Trello, when2meet, etc.). The
credibility movement seems to suggest that by having both collaborations
that span across the globe and subfields of research areas, age groups,
and education levels should help to drive science in the path of better
materials, reliability, generalizability and more robust sample sizes
(when necessary) in a study [@auspurg2021; @nosek2014method;
@lebel2018].

### 2023-08-29 manuscript_scopus.tex
typo

BTS appears to be expanding as a result of two sources: 1) increasing
globalization and technology that allows for real-time interdisciplinary
research, and 2) expanding interest in reproducibility, replication, and
generalizability\textsuperscript{5--7}. Technological
advances have provided easier ways to collaborate with people who are
from other universities and countries through document sharing platforms
(e.g., Google, GitHub, and the Open Science Framework), video chatting
platforms (e.g., Zoom, Microsoft Teams), and messaging and project
management platforms (e.g., Slack, Trello, when2meet, etc.). The
credibility movement seems to suggest that by having both collaborations
that span across the globe and subfields of research areas, age groups,
and education levels should help to drive science in the path of better
materials, reliability, generalizability and more robust sample sizes
(when necessary) in a study\textsuperscript{8};\textsuperscript{9};\textsuperscript{10}{]}.

>>>>

BTS appears to be expanding as a result of two sources: 1) increasing
globalization and technology that allows for real-time interdisciplinary
research, and 2) expanding interest in reproducibility, replication, and
generalizability\textsuperscript{5--7}. Technological
advances have provided easier ways to collaborate with people who are
from other universities and countries through document sharing platforms
(e.g., Google, GitHub, and the Open Science Framework), video chatting
platforms (e.g., Zoom, Microsoft Teams), and messaging and project
management platforms (e.g., Slack, Trello, when2meet, etc.). The
credibility movement seems to suggest that by having both collaborations
that span across the globe and subfields of research areas, age groups,
and education levels should help to drive science in the path of better
materials, reliability, generalizability and more robust sample sizes
(when necessary) in a study\textsuperscript{8--10}.
